Regional Inequalities and economic growth; cross section and times series analysis

### 2023-11-22 MSB104_GR_1_Final_Assignment_research_article.qmd
:D

By exploring our pervious estimates in the relationship between regional development on regional inequality we will estimate the log of GDP per capita in a liner regression model, defining the variables as new determinants on the effects in regional economic development using logarithim of GDP per capita.

Firstly, we will divide the data into different subsets. Using France (x) as a binary value often called a dummy variable. France is chosen since it is the country with the most observations in 2010. Dummy variables are used to explain qualitative variables in regression models [@wooldridge2020].

@@

```{r}
# Logarithmic model

>>>>

By exploring our previous estimates in the relationship between regional development on regional inequality we will estimate the log of GDP per capita in a liner regression model, defining the variables as new determinants on the effects in regional economic development using logarithim of GDP per capita.

Firstly, the data is devided into different subsets. Using France (x) as a binary value also called a dummy variable [@wooldridge2020].

@@

```{r}
#| echo: false
#| output: false
# Logarithmic model
